### 2010-03-04 byu_studies/poster.tex
Finished the poster for BYU Studies

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Some math symbols used in the text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Format 
\newcommand{\Matrix}[1]{\begin{bmatrix} #1 \end{bmatrix}}
\newcommand{\Vector}[1]{\Matrix{#1}}
\newcommand*{\SET}[1]  {\ensuremath{\mathcal{#1}}}
\newcommand*{\MAT}[1]  {\ensuremath{\mathbf{#1}}}
\newcommand*{\VEC}[1]  {\ensuremath{\bm{#1}}}
\newcommand*{\CONST}[1]{\ensuremath{\mathit{#1}}}
\newcommand*{\norm}[1]{\mathopen\| #1 \mathclose\|}% use instead of $\|x\|$
\newcommand*{\abs}[1]{\mathopen| #1 \mathclose|}% use instead of $\|x\|$
\newcommand*{\absLR}[1]{\left| #1 \right|}% use instead of $\|x\|$

\def\norm#1{\mathopen\| #1 \mathclose\|}% use instead of $\|x\|$
\newcommand{\normLR}[1]{\left\| #1 \right\|}% use instead of $\|x\|$

@@

\definecolor{lightblue}{cmyk}{.3,0,0,0.0}
\definecolor{lighterblue}{cmyk}{.2,0,0,0.0}
\definecolor{lightestblue}{cmyk}{.1,0,0,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighterblue,
  bgColorTwo=lightestblue,
  borderColor=reddishblue,
  headerColorOne=blue,
  headerColorTwo=reddishblue,
  headerFontColor=black,
  boxColorOne=lightblue,
  boxColorTwo=lighterblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
  background=shade-tb,
  %background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Automatic Topic Discovery in 100 Years of General Conference Talks}
  % Authors
  {\sf %Sans Serif
  % Serif
  Matthew Gardner
  (mjg82@byu.edu)
  and
  Eric Ringger
  (ringger@cs.byu.edu)
  }
  % University logo
  {{\begin{minipage}{16em}
    \hfill
    \includegraphics[height=5.5em]{byunlp.eps}
  \end{minipage}}
  }

@@

	\begin{centering}
	  \psfrag{b}[C][C]{\huge$\beta$}
	  \psfrag{a}[C][C]{\huge$\alpha$}
	  \psfrag{t}[C][C]{\huge$\theta$}
	  \psfrag{f}[C][C]{\huge$\phi$}
	  \psfrag{w}[C][C]{\huge$w$}
	  \psfrag{z}[C][C]{\huge$z$}
	  \psfrag{N}[C][C]{\Large$N$}
	  \psfrag{M}[C][C]{\Large$M$}
	  \psfrag{K}[C][C]{\Large$K$}
	  \includegraphics[height=.82\linewidth]{lda_model.eps}
	  \begin{align*} 
		w_i|z_i,\phi^{(z_i)} &\sim \mathrm{Categorical}(\phi^{(z_i)}) \\
		\phi &\sim \mathrm{Dirichlet}(\beta) \\
		z_i|\theta^{(d_i)} &\sim \mathrm{Categorical}(\theta^{(d_i)}) \\ 
		\theta &\sim \mathrm{Dirichlet}(\alpha) 
	  \end{align*}
	\end{centering}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results}
  {name=results word distributions,column=1,span=2,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	The main result of using LDA is a list of which words are most likely to be
	used in each topic.  In the algorithm, the topics just have numbers; the
	computer merely looks for statistical relationship between words.  The
	labels are thus our own.  We present here a few of the topics we found.

	\small
	\begin{center}
	  \begin{tabular}{ccccc}
		Topic 19: Tithing&Topic 33: Welfare&Topic 52: Women&Topic 37: Families
		&Topic 7: Government\\
		\hline
		tithing&welfare&women&children&government \\
		pay&poor&society&home&united \\
		money&church&relief&family&liberty \\
		debt&fast&sisters&parents&nation \\
		means&help&hinckley&teach&states \\
		out&services&each&child&country \\
		people&program&b&families&freedom \\
		one&plan&gordon&homes&land \\
		paid&care&lives&love&free \\
		poor&needs&service&mother&men \\
		tithes&food&sister&taught&constitution \\
		get&need&forward&fathers&people \\
		more&family&strength&responsibility&america \\
	  \end{tabular}
	\end{center}

	\normalsize
	\mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\
	Because each talk has a date associated with it, we can use LDA to analyze
	the distribution of these topics over time, seeing at when certain topics
	were most discussed.  In doing this, we see clear correlations with
	real-world occurrences.

	\begin{center}
	  \includegraphics[height=.34\linewidth]{topic19.eps}
	  \includegraphics[height=.34\linewidth]{topic33.eps}

	  \includegraphics[height=.34\linewidth]{topic52.eps}
	  \includegraphics[height=.34\linewidth]{topic56.eps}
	\end{center}

  }%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Future Work}{name=future work,column=3,span=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	We have used natural language processing techniques on a novel data
	source---LDS General Conference talks.  However, our exploration of the
	results has been quite preliminary.  Our research lays the groundwork for a
	more thorough analysis of religious discourse in the LDS Church.  These
	techniques allow us to quickly answer questions such as, ``Which topics are
	constant over time, and which come and go?'' and ``Which years had the
	highest diversity of topics, and which were more narrow-focused?''

	We also have only considered General Conference talks.  A fruitful avenue
	of future work would be to compare the results of our techniques on many
	different corpora of LDS religious and scholarly texts, such as the Journal
	of Discourses, the Book of Mormon, the Doctrine and Covenants, the
	collected works of Hugh Nibley, or the past 50 years of BYU Studies.  Such
	analysis could broaden our understanding of and appreciation for our
	textual history.

  }%

\end{poster}%
%
\end{document}

>>>>

@@

\definecolor{lightblue}{cmyk}{.3,0,0,0.0}
\definecolor{lighterblue}{cmyk}{.2,0,0,0.0}
\definecolor{lightestblue}{cmyk}{.1,0,0,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighterblue,
  bgColorTwo=lightestblue,
  borderColor=reddishblue,
  headerColorOne=blue,
  headerColorTwo=reddishblue,
  headerFontColor=black,
  boxColorOne=lightblue,
  boxColorTwo=lighterblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=yes,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
  background=shade-tb,
  %background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {{\begin{minipage}{7em}
    \includegraphics[height=5em]{amllogo.eps}
  \end{minipage}}
  }
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Automatic Topic Discovery in 100 Years of General Conference Talks}
  % Authors
  {\sf %Sans Serif
  % Serif
  Matthew Gardner
  (mjg82@byu.edu)
  and
  Eric Ringger
  (ringger@cs.byu.edu)
  }
  % University logo
  {{\begin{minipage}{7em}
    \hfill
    \includegraphics[height=5em]{byunlp.eps}
  \end{minipage}}
  }

@@

	\begin{centering}
	  \psfrag{b}[C][C]{\Large$\beta$}
	  \psfrag{a}[C][C]{\Large$\alpha$}
	  \psfrag{t}[C][C]{\Large$\theta$}
	  \psfrag{f}[C][C]{\Large$\phi$}
	  \psfrag{w}[C][C]{\Large$w$}
	  \psfrag{z}[C][C]{\Large$z$}
	  \psfrag{N}[C][C]{\large$N$}
	  \psfrag{M}[C][C]{\large$M$}
	  \psfrag{K}[C][C]{\large$K$}
	  \includegraphics[height=.485\linewidth]{lda_model.eps}
	  \begin{align*} 
		M &= \mathrm{Number\ of\ documents} \\
		N &= \mathrm{Number\ of\ words\ in\ a\ document} \\
		K &= \mathrm{Number\ of\ topics} \\
		w &= \mathrm{Word\ in\ a\ document} \\
		z &= \mathrm{Topic\ corresponding\ to\ word\ } w \\
		w_i|z_i,\phi^{(z_i)} &\sim \mathrm{Categorical}(\phi^{(z_i)}) \\
		\phi &\sim \mathrm{Dirichlet}(\beta) \\
		z_i|\theta^{(d_i)} &\sim \mathrm{Categorical}(\theta^{(d_i)}) \\ 
		\theta &\sim \mathrm{Dirichlet}(\alpha) 
	  \end{align*}
	\end{centering}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results: Topic--Word Distributions}
  {name=words,column=1,span=2,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	The main result of using LDA is a list of which words are most likely to be
	used in each topic.  In the algorithm, the topics just have numbers; the
	computer merely looks for statistical relationships between words.  Even
	so, the topics are easily distinguishable.  We present here a few of the
	topics we found.

	\begin{center}
	  \begin{tabular}{cccccccc}
		Topic 19&Topic 33&Topic 52&Topic 37&Topic 7&Topic 26&Topic 28&Topic 22\\
		\hline
		tithing&welfare&women&children&government&see&years&true \\
		pay&poor&society&home&united&d&one&honest \\
		money&church&relief&family&liberty&c&two&good \\
		debt&fast&sisters&parents&nation&1&hundred&integrity \\
		means&help&hinckley&teach&states&2&five&virtue \\
		out&services&each&child&country&3&three&character \\
		people&program&b&families&freedom&s&thousand&honesty \\
		one&plan&gordon&homes&land&ne&twenty&without \\
		paid&care&lives&love&free&4&ago&one \\
		poor&needs&service&mother&men&5&four&men \\
		tithes&food&sister&taught&constitution&alma&year&honor \\
		get&need&forward&fathers&people&6&six&respect \\
		more&family&strength&responsibility&america&7&over&god \\
	  \end{tabular}
	\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results: Topics over Time}
  {name=results topics over time,column=1,span=2,below=words}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	Because each talk has a date associated with it, we can use LDA to analyze
	the distribution of these topics over time, seeing at what points certain
	topics were most discussed.  In doing this, we see clear correlations with
	real-world occurrences.

	\begin{center}
	  \includegraphics[height=.305\linewidth]{topic19.eps}
	  \includegraphics[height=.305\linewidth]{topic33.eps}

	  \includegraphics[height=.305\linewidth]{topic52.eps}
	  \includegraphics[height=.305\linewidth]{topic56.eps}
	\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results: Topics by Speaker}
  {name=speaker,column=3,span=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	Because each talk has a speaker, we can look at topics to see who was most
	likely to use them in their talks.  Again we see here that our automatic
	analysis is validated by real-world occurrences.

	\begin{center}
	  \begin{tabular}{cc}
		Relief Society Topic&Sunday School Topic\\
		\hline
		Sister Barbara B. Smith&Karl G. Maeser \\
		Mary Ellen W. Smoot&George Reynolds \\
		Mary Ellen Smoot&E. C. Phillips \\
		Elaine L. Jack&Josiah H. Burrows \\
		Marian R. Boyer&George Goddard \\
		Virginia U. Jensen&Joseph J. Jackson\\
		Wayne M. Hancock&L. John Nuttall \\
		Shirley W. Thomas&Sunday School Union \\
		Bonnie D. Parkin&John D. Peters \\
		Kathleen H. Hughes&Joseph Jackson \\
		Sheri L. Dew&George Q. Cannon \\
		Richard H. Winkel&Heber J. Grant \\
		Aileen H. Clyde&Joseph Summerhays \\
	  \end{tabular}
	\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Future Work}{name=future work,column=3,span=1,below=speaker}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	We have used natural language processing techniques on a novel data
	source---LDS General Conference talks.  However, our exploration of the
	results has been quite preliminary.  Future areas of research could 
	include:
	\begin{itemize}
	  \item A more thorough analysis of religious discourse in the LDS Church,
		answering questions such as ``Which topics are constant over time, and
		which come and go?''
	  \item Explore other religious and scholarly LDS texts, including the
		Journal of Discourses, the Book of Mormon, the Doctrine and Covenants,
		the collected works of Hugh Nibley, or the past 50 years of BYU
		Studies.
	  \item Not only explore other data sets in isolation, but compare them;
		see how the past 100 years of General Conference differs from the
		previous 100 years in the Journal of Discourses.
	  \item The use of other natural language processing techniques to analyze
		the data.  Possibilities include Topical N-grams, an extension of LDA
		that returns strings of words in the topic instead of isolated words.
	\end{itemize}

\end{poster}

\end{document}
